Supporting information: Copulas and their potential for ecology

### 2019-10-22 SupportingInformation.Rmd
ready to submit, I think

---
title: "Supporting information: Copulas and their potential for ecology"
author: "Shyamolina Ghosh, Lawrence W. Sheppard, Mark T. Holder, Terrance E. Loecke, Philip C. Reid, James D. Bever, Daniel C. Reuman"
geometry: "left=1cm,right=1cm,top=2.2cm,bottom=2.2cm"

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm,height=8 cm]{./Results/copula_pedagog_fig_BB1.pdf}
\caption[Lower- and upper-tail dependence can vary independently of correlation]{Lower- and 
upper-tail dependence can vary independently of correlation. (A-C) Data generated using the BB1 
copula (see Background section in the main text) 
with three different 
sets of parameters chosen to produce a variety of 
lower-tail (LT) and upper-tail (UT) dependence strengths, but with the same 
Kendall correlation (K) (to two digits) in all cases. (D-F) Similar to A-C, but
with stronger correlation. Asymmetry of tail dependence (LT-UT) is the same 
within each column. See Background section in the main text for a formal description of 
tail dependence and other measures of association in the tails.\label{fig_cop_pedag}}
\end{center}
\end{figure}

@@

# Spatial resampling with multivariate datasets for nonparametric statistics \label{spatial_resamp}
<!--***DAN: leave this section exactly as it is, but it may be out of order
now that we describe how this is done in the methods. In fact, I think I
have to do this more generally.-->

@@

<!--Displaying summary table with model selection results from asymmetric dependence analysis-->
<!--Decided to remove this from the AER version
```{r tab_summary_stat_asym_sens,echo=F,results="markup"}
summary_stat<-summary_stat[c(1:6),]
rownames(summary_stat)<-c("Best-fit copula AICw","Normal copula AICw","Model-avg. LT","Model-avg. UT","p, CvM","p, KS")
knitr::kable(summary_stat, booktabs = T, escape=F,
             format = "latex", linesep = "",
             digits=4, col.names=c("b=0.1, g$_{1}$","b=0.1, g$_{2}$",
                                   "b=-0.1, g$_{1}$","b=-0.1, g$_{2}$",
                                   "b=0.5, g$_{1}$","b=0.5, g$_{2}$",
                                   "b=-0.5, g$_{1}$","b=-0.5, g$_{2}$"),
      caption.short="Asymmetric sensitivity model, model selection results",
      caption="Asymmetric sensitivity model, model selection results. 
The output of simulations from the first model detailed in 
the methods section for Q2 (i.e., Figs \\ref{MT-fig_ms_asym_b_0.1} and 
\\ref{fig_ms_asym_b_-0.1_0.5_-0.5}) were subjected to the model 
selection procedures detailed in the 
methods section for Q1. Best-fit copula AICw: the AIC weight of the best-fitting copula family;
Normal copula AICw: the AIC weight of the normal copula family; Model-avg. LT: the lower-tail 
statistic, weighted-averaged across models using AICw; Model-avg. UT: same, but for the 
upper-tail statistic; p, CvM: p-value for goodness of fit test of the best-fitting copula
family using the test based on the Cramer-von Mises statistic; p, KS: p-value for goodness of fit 
test of the best-fitting copula family using the test based on the Kolmogorov-Smirnov 
statistic.\\label{tab_summary_stat_asym_sens}")
```
-->

>>>>

---
title: "Supporting information: Copulas and their potential for ecology"
author: "Shyamolina Ghosh, Lawrence W. Sheppard, Mark T. Holder, Terrance D. Loecke, Philip C. Reid, James D. Bever, Daniel C. Reuman"
geometry: "left=1cm,right=1cm,top=2.2cm,bottom=2.2cm"

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm,height=8 cm]{./Results/copula_pedagog_fig_BB1.pdf}
\caption[Lower- and upper-tail dependence can vary independently of correlation]{Lower- and 
upper-tail dependence can vary independently of correlation. (A-C) Data generated using the BB1 
copula (see section \ref{MT-Background} in the main text) 
with three different 
sets of parameters chosen to produce a variety of 
lower-tail (LT) and upper-tail (UT) dependence strengths, but with the same 
Kendall correlation (K) (to two digits) in all cases. (D-F) Similar to A-C, but
with stronger correlation. Asymmetry of tail dependence (LT-UT) is the same 
within each column. See section \ref{Background} in the main text for a formal description of 
tail dependence and other measures of association in the tails.\label{fig_cop_pedag}}
\end{center}
\end{figure}

@@

# Spatial resampling with multivariate datasets for nonparametric statistics \label{spatial_resamp}

@@

<!--Displaying summary table with model selection results from asymmetric dependence analysis-->
<!--Decided to remove this from the AER version
```{r tab_summary_stat_asym_sens,echo=F,results="markup"}
summary_stat<-summary_stat[c(1:6),]
rownames(summary_stat)<-c("Best-fit copula AICw","Normal copula AICw","Model-avg. LT","Model-avg. UT","p, CvM","p, KS")
knitr::kable(summary_stat, booktabs = T, escape=F,
             format = "latex", linesep = "",
             digits=4, col.names=c("b=0.1, g$_{1}$","b=0.1, g$_{2}$",
                                   "b=-0.1, g$_{1}$","b=-0.1, g$_{2}$",
                                   "b=0.5, g$_{1}$","b=0.5, g$_{2}$",
                                   "b=-0.5, g$_{1}$","b=-0.5, g$_{2}$"),
      caption.short="Asymmetric sensitivity model, model selection results",
      caption="Asymmetric sensitivity model, model selection results. 
The output of simulations from the first model detailed in 
section \\ref{Causes} of the main text (i.e., Figs \\ref{MT-fig_ms_asym_b_0.1} and 
\\ref{fig_ms_asym_b_-0.1_0.5_-0.5}) were subjected to the model 
selection procedures detailed in section \\ref{Methods} of the main text. 
Best-fit copula AICw: the AIC weight of the best-fitting copula family;
Normal copula AICw: the AIC weight of the normal copula family; Model-avg. LT: the lower-tail 
statistic, weighted-averaged across models using AICw; Model-avg. UT: same, but for the 
upper-tail statistic; p, CvM: p-value for goodness of fit test of the best-fitting copula
family using the test based on the Cramer-von Mises statistic; p, KS: p-value for goodness of fit 
test of the best-fitting copula family using the test based on the Kolmogorov-Smirnov 
statistic.\\label{tab_summary_stat_asym_sens}")
```
-->
